Supplement to ``{\mytitle}''

### 2023-09-11 si/calibrateMod3.Rnw
Removed unused ncores argument

haiti3_sub_fit <- bake(
  file = "../model3/si/subset_noparams.rds", {
    fit_haiti3(
      nsearches = 2L,
      search1 = SEARCH1,
      search2 = SEARCH2,
      search_rho = FALSE,
      search_gamma = FALSE,
      search_Iinit = FALSE,
      search_hur = FALSE,
      ncores = cores
    )
  }
)

>>>>

haiti3_sub_fit <- bake(
  file = "../model3/si/subset_noparams.rds", {
    fit_haiti3(
      nsearches = 2L,
      search1 = SEARCH1,
      search2 = SEARCH2,
      search_rho = FALSE,
      search_gamma = FALSE,
      search_Iinit = FALSE,
      search_hur = FALSE
    )
  }
)
